### 2024-11-14 conteudo/tool/tool.tex
add arkanjo as tool name

Our proposed tool is a Command Line Interface (CLI) application designed to
help developers identify code clone duplication at the function level.
Specifically, it enables the detection of pairs of functions within a codebase
that are clones of each other.

@@

The tool has been implemented and is available for reference at
\url{https://github.com/LipArcanjo/test-duplication-code}.

>>>>

Arkanjo, our proposed tool, is a Command Line Interface (CLI) application designed to
help developers identify code clone duplication at the function level.
Specifically, it enables the detection of pairs of functions within a codebase
that are clones of each other.

@@

The Arkanjo tool has been implemented and is available for reference at
\url{https://github.com/LipArcanjo/arkanjo}.
